State change and diversity animations

### 2022-11-24 reports/animations/report.Rmd
update animation report

---
title: "State change and diversity animations"
author: "Owen Petchey"
date: "6/1/2022"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

>>>>

---
title: "State change and diversity animations"
author: "Owen Petchey"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---
